\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
trying to pull

	 \begin{definition}[Coherent subspace]\label{def:cohspace}
	 	The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints holds for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
	 \end{definition}

     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.  The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e. $m=2$ and $n=3$.  It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.  In Figure \ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.  However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.  However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

     \begin{figure}[H]
     	\centering
     	\vspace{-0.9cm}
     	\small
     	\resizebox{\linewidth}{!}{
     		\input{Figs/3D_hierarchy}
     	}
     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$. The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
     \end{figure}

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure\ref{fig:basichier} and/or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with weird overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

	Figure \ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure \ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

@@

	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general. To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e. $\mathfrak{L}\subset\mathfrak{s}$. Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$. This is depicted in Figure \ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.  In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.

@@

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.  \todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.  Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.  This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.

	Our own solution to dealing with biased forecasts is to bias correct {\em before} reconciliation.  In many cases the method for bias correction will be context specific.  For instance, in  our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where bias is induced via taking a Box-Cox transformation before modelling.  In this well-known case a number of bias correction methods exist.  Our particular choice of bias correction will be the Guererro method \citep{guerrero1993time}.

@@

	\begin{equation} \label{eq:BoxCox_BT_biasadj}
	 y_{t+h} = 
	\begin{cases} 
	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if log transformation, $\lambda = 0$} \\
	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if Box-Cox transformation, $\lambda \ne 0$}
	\end{cases}
	\end{equation}
	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the log/Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$. Unbiased forecasts from this method is referred to as Unbiased (Method-1). We also applied a more general bias adjustment method by estimating the bias using in-sample residual means as explained in Section \ref{sec:BiasInRecon}. Unbiased forecasts from this general method is referred to as Unbiased (Method-2).\todo{Should we give more concise words for these two methods??}

@@

\begin{table}
	\caption {Average {MSE($\times 10^3$)} of base and reconciled $1$-step-ahead point forecasts are presented for log transformation and Box-Cox transformation. Unbiased(Method-1) follows from the bias adjustment via Taylor's de-biasing factor whereas Unbiased(Method-2) follows from residual mean adjustment.} 
	\label{tab:Results_MSE}
	\centering

	\resizebox{\linewidth}{!}{
		\begin{tabular}{@{}lcccccc@{}}
			\toprule
			\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
			\multicolumn{3}{c}{Box-Cox Transformation}\\
			\cmidrule(lr){2-4} \cmidrule(lr){5-7}
			R.method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
			& & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\
			\midrule
			Base & 12.06 & 11.87 & 12.52 & 12.27 & 139.94 & 13.45\\
			\hline
			Bottom-up & 17.37 & 15.47 & 21.58 & 18.06 & 15.76 & 23.33\\
			\hline
			OLS & 11.59 & 11.41 & 11.98 & 11.84 & 116.91 & 12.96\\
			\hline
			WLS & 15.00 & 13.83 & 17.55 & 15.83 & 14.20 & 19.51\\
			\hline
			MinT(Shrink) & 9.36 & $\bm{9.25}$ & 10.35 & 10.27 & $\bm{10.11}$ & 12.43\\
			\bottomrule
		\end{tabular}
	}

@@

%	Following the distance reducing property in Theorem \ref{th:distred} and the discussion therein, we have noted that the orthogonal projections will always improve the base forecasts with respect to the mean squared errors whereas, the oblique projections will not always, but improves only on average. Figure \ref{fig:BaseVSRecon_Fc} shows the MSE difference between base forecasts and reconciled forecasts - MinT, OLS and WLS for all replications in different forecast horizons. Recall that OLS reconciliation is doing orthogonal projection whereas MinT and WLS are doing oblique projections onto the coherent subspace. It is apparent from the plot that the MSE difference for OLS is always positive, implying that OLS improves the base in terms of MSE in all replications. On the other hand,  there are some instances that this difference for MinT and WLS is negative which is reflected from the short negative tails of box-plots. This implies that oblique projections will not improve the base forecasts in every case. However, these projections will outperform the base with respect to MSE on average which is again reflected from the highly positive skewed MSE differences.

>>>>

	 \begin{definition}[Coherent subspace]\label{def:cohspace}
	 	The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints holds for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
	 \end{definition}
     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.  The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e. $m=2$ and $n=3$.  It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.  In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.  However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom-level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.  However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

     \begin{figure}[H]
     	\centering
     	\vspace{-0.9cm}
     	\small
     	\resizebox{\linewidth}{!}{
     		\input{Figs/3D_hierarchy}
     	}
     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that span $\mathfrak{s}$. The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
     \end{figure}

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation. Examples include, temporal hierarchies which involve grouped structures \citep[see][]{AthEtAl2017}, overlapping temporal hierarchies \citep[see][]{JeoEtAl2019}, applications for which the difference rather than the aggregate is of interest \cite[see][]{LiTan2019}, or structures that involve both cross-sectional and temporal dimensions referred to as cross-temporal structures \citep[see][]{KouAth2019}. Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection shown in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts an oblique projection along $\bm{R}$ for all the gray points, yielding reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of the reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

@@

	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general. To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e. $\mathfrak{L}\subset\mathfrak{s}$. Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$. This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.  In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.

@@

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix. However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.  Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.  This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance is to reduce variance.

    \subsection{Bias correction}

	Our own solution to dealing with biased forecasts is to bias correct {\em before} reconciliation.  In many cases the method for bias correction will be context specific.  For instance, in  our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where bias is induced via taking a Box-Cox transformation before modelling.  In this well-known case a number of bias correction methods exist.  Our particular choice of bias correction will be the Guererro method \citep{guerrero1993time}. \textcolor{red}{TODO: Read this again after the empirical application has been completed. I am saying this because my understanding is that we use the Guererro method to choose the lambda for the BoxCox transformation. Then we back transform the forecasts using the same lambda once with bias correcting using the factor that comes out of a Taylor series expansion around $\mu$ (programmed in fable/forecast package) and once without it hence looking at medians and not means - hence biased base forecasts. If my understanding here is correct I am not sure we can say we are using the Guererro method to bias correct.}

@@

	\begin{equation} \label{eq:BoxCox_BT_biasadj}
	 y_{t+h} =
	\begin{cases}
	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if } \lambda = 0 \\
	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if } \lambda \ne 0
	\end{cases}
	\end{equation}
	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$.

@@

\begin{table}
	\caption {Average {MSE($\times 10^3$)} of base and reconciled $1$-step-ahead point forecasts are presented for log transformation and Box-Cox transformation. Unbiased(Method-1) follows from the bias adjustment via Taylor's de-biasing factor whereas Unbiased(Method-2) follows from residual mean adjustment.} 
	\label{tab:Results_MSE}
	\centering
	\resizebox{\linewidth}{!}{
		\begin{tabular}{@{}lcccccc@{}}
			\toprule
			\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
			\multicolumn{3}{c}{Box-Cox Transformation}\\
			\cmidrule(lr){2-4} \cmidrule(lr){5-7}
			R.method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
			& & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\
			\midrule
			Base & 12.06 & 11.87 & 12.52 & 12.27 & 139.94 & 13.45\\
			\hline
			Bottom-up & 17.37 & 15.47 & 21.58 & 18.06 & 15.76 & 23.33\\
			\hline
			OLS & 11.59 & 11.41 & 11.98 & 11.84 & 116.91 & 12.96\\
			\hline
			WLS & 15.00 & 13.83 & 17.55 & 15.83 & 14.20 & 19.51\\
			\hline
			MinT(Shrink) & 9.36 & $\bm{9.25}$ & 10.35 & 10.27 & $\bm{10.11}$ & 12.43\\
			\bottomrule
		\end{tabular}
	}

@@
